\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2.5\baselineskip}

### 2016-07-20 document/ms.tex
Adding refs to Mullally

In this \paper, we develop a systematic method for reliably discovering the
transits of large, long-period companions in photometric time series
\emph{without human intervention}.
Since the search methodology is fully automated, we can robustly measure the
search completeness~--~using injection and recovery tests~--~and use these
products to place probabilistic constraints on the occurrence rate of
long-period planets.
We apply this method to a subset of the archival data from the \kepler\
Mission, present a catalog of exoplanet candidates, and estimate the
occurrence rate of long-period exoplanets.
We finish by discussing the potential effects of false positives, evaluating the
prospects for follow-up, and comparing our results to other studies
based on different planet discovery methods.

@@

In this step of the method, the goal is to discard any signals that are not
sufficiently ``transit-like'' in shape.
To quantify this decision, we perform a model comparison between a physical
transit model and a set of other parameterized models for systematics.
In order for a candidate to pass this vetting step, the transit model must be
``preferred'' to any other model as measured using the Bayesian Information
Criterion (BIC).
The BIC is not the optimal choice for this model comparison, but it is
more computationally computationally tractable than the alternatives, such
as computing thousands of precise marginalized
likelihoods or expected utilities for each model.
The BIC can be efficiently computed and it exhibits the desired
behavior~--~decreasing with increasing likelihood but flexible models are
penalized~--~and we find that it performs sufficiently well in practice.

@@

\dfmtodo{More words here about comparison and interpretation.}

@@

\vspace{1.5em}
All of the code used in this project is available from
\url{https://github.com/dfm/peerless} under the MIT open-source software
license.
This code (plus some dependencies) can be run to re-generate all of the
figures and results in this \paper; this version of the paper was generated
with git commit \texttt{\githash} (\gitdate).
The parameter estimation results are available for download as MCMC samplings
on Zenodo at \datareleaseurl.

>>>>

In this \paper, we develop a systematic method for reliably discovering the
transits of large, long-period companions in photometric time series
\emph{without human intervention}.
The method is similar in character to the recently published fully automated
method used to generate the official DR24 exoplanet candidate catalog from
\kepler\ \citep{Mullally:2016, Coughlin:2016}.
Since the search methodology is fully automated, we can robustly measure the
search completeness~--~using injection and recovery tests~--~and use these
products to place probabilistic constraints on the occurrence rate of
long-period planets.
We apply this method to a subset of the archival data from the \kepler\
Mission, present a catalog of exoplanet candidates, and estimate the
occurrence rate of long-period exoplanets.
We finish by discussing the potential effects of false positives, evaluating the
prospects for follow-up, and comparing our results to other studies
based on different planet discovery methods.

@@

In this step of the method, the goal is to discard any signals that are not
sufficiently ``transit-like'' in shape.
This step is similar to the method independently developed and recently
published by the \kepler\ team \citep{Mullally:2016}.
To quantify the quality of a candidate, we perform a model comparison between
a physical transit model and a set of other parameterized models for
systematics.
In order for a candidate to pass this vetting step, the transit model must be
``preferred'' to any other model as measured using the Bayesian Information
Criterion (BIC).
The BIC is not the optimal choice for this model comparison, but it is more
computationally computationally tractable than the alternatives, such as
computing thousands of precise marginalized likelihoods or expected utilities
for each model.
The BIC can be efficiently computed and it exhibits the desired
behavior~--~decreasing with increasing likelihood but flexible models are
penalized~--~and we find that it performs sufficiently well in practice.

@@

% \dfmtodo{More words here about comparison and interpretation.}

@@

\vspace{1.5em}
All of the code used in this project is available from
\url{https://github.com/dfm/peerless} under the MIT open-source software
license.
This code (plus some dependencies) can be run to re-generate all of the
figures and results in this \paper; this version of the paper was generated
with git commit \texttt{\githash} (\gitdate).
The parameter estimation results represented as MCMC samplings and the
injection results are available for download from Zenodo at \datareleaseurl.
